### 2023-10-06 README.Rmd
badges included - 231006

[![R-CMD-check](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
and can also predict outside tasks that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study, you have to program these on your own. Since the start of

>>>>

[![R-CMD-check](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml)

[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC is valid
and can also predict outside tasks that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study, you have to program these on your own.

> Currently <code>validateHOT</code> only works with data from Sawtooth Software 
due to the coding of price.
